---
title: "Research"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## working papers
- __Value-Added Tax and Shadow Economy: The Role of Input-Output Linkages__ [link](http://papers.ssrn.com/sol3/papers.cfm?abstract_id=2291867)

- __Finance and Poverty: Evidence from India,__ with Meghana Ayyagari and Thorsten Beck [link](http://papers.ssrn.com/sol3/papers.cfm?abstract_id=2275150),  [Vox column summary](http://www.voxeu.org/article/migrating-out-poverty-role-finance)


- __Informality and Access to Finance: Evidence from India,__ with Thorsten Beck [link](http://papers.ssrn.com/sol3/papers.cfm?abstract_id=2491466)

- __Misreporting of VAT and Optimal Enforcement__ [link](http://papers.ssrn.com/sol3/papers.cfm?abstract_id=2505998)

- __Trade credit and access to finance of retailers in Ethiopia,__ with Thorsten Beck and Burak Uras [link](https://assets.publishing.service.gov.uk/media/5aaa440fed915d4f595c5a67/Beck_et_al_Trade_credit_in_Ethiopia.pdf)

- __VAT reform, Distortions, and Informality: Evidence from Indian States,__ with Oceane Briand.




```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
