---
title: "Research"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## working papers
- __Finance and Poverty: Evidence from India,__ with Meghana Ayyagari and Thorsten Beck, <http://papers.ssrn.com/sol3/papers.cfm?abstract_id=2275150>
  - Vox column summary: <http://www.voxeu.org/article/migrating-out-poverty-role-finance>

- __Value-Added Tax and Shadow Economy: The Role of Input-Output Linkages,__ <http://papers.ssrn.com/sol3/papers.cfm?abstract_id=2291867>


- __Informality and Access to Finance: Evidence from India,__ with Thorsten Beck, <http://papers.ssrn.com/sol3/papers.cfm?abstract_id=2491466>

- __Misreporting of VAT and Optimal Enforcement,__ <http://papers.ssrn.com/sol3/papers.cfm?abstract_id=2505998>

- __Trade credit and access to finance of retailers in Ethiopia,__ with Thorsten Beck and Burak Uras. DFID Working Paper.

- __VAT reform, Distortions, and Informality: Evidence from Indian States,__ with Oceane Briand.




```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
